Online Verification of Commutativity

### 2020-06-11 acmPaper/paper.tex
better evaluation for currency graph.

We allowed an "error tolerance" for floating point error.
Graphs were generally found to be consistent up to an error tolerance to the order of magnitude $10^{-6}$.
However, below this threshold we found inconsistencies.
Averaging over evaluation for the first 9 days of 2020, verifying and building a graph to completion (inclusive of the time required by network calls) took 223$\pm$34 seconds using algorithm ~\ref{optimal}, and in 128$\pm$7 seconds with algorithm ~\ref{polynomial}. 
Computation was performed on a Macbook Pro 2015, 2.9 GHz Dual-Core Intel Core i5.
More information about implementation can be found in the evaluation section.

>>>>

We allowed an "error tolerance" for floating point error.
Graphs were generally found to be consistent up to an error tolerance to the order of magnitude $10^{-6}$.
However, below this threshold we found inconsistencies.
Averaging over evaluation for the first 30 days of 2020, building and verifying a diagram to completion (inclusive of the time required by network calls) took 243$\pm$19 seconds using algorithm ~\ref{optimal}, and in 133$\pm$13 seconds with algorithm ~\ref{polynomial}. 
Computation was performed on a Macbook Pro 2015, 2.9 GHz Dual-Core Intel Core i5.
More information about implementation can be found in the evaluation section.
